Species persistence under climate and fishing

### 2014-01-28 Writing/MS.tex
Working on catch story, updated Malin's comments

\begin{spacing}{1.9}
\begin{flushleft}

@@

We added harvesting pressure by harvesting a constant proportion of the population, in order to confirm our analytical results. We extended our work by evaluating the effect of a threshold harvest rule and marine protected 
areas (MPAs). With a threshold rule, we evaluated the population at each point in space to determine how 
much harvesting should occur. If the population abundance was below the designated threshold, no 
harvesting occurred. If the population exceeded the threshold, then a proportion of the `surplus' individuals 
were harvested. To implement an MPA management strategy, we used two commonly advocated approaches: 
MPAs designed to improve fisheries yields and MPAs designed for primarily for conservation [REFS]. These networks 
of MPAs were introduced into our simulations by designating segments of space in which harvesting was 
forbidden (i.e.~harvesting rates were equal to $0$). The conservation MPAs had a length of 4 times the average 
dispersal distance and had a distance of 8 times the average dispersal distance between them. Fisheries MPAs had a length of 1/3 of the 
average dispersal distance and had a distance of 2/3 of the average dispersal distance between them. These distances were chosen for the following reasons: the goal of conservation-oriented MPAs is to protect source populations, ideally that are self sustaining under a static climate. Fisheries MPAs are focused on maximizing spillover of fish populations into fishable waters, thus many MPAs, each of which are smaller than the average dispersal distance, replicates this high spillover effect.

@@

We found that thresholds of any amount alleviate the effects of harvesting, and the ability of the population to 
persist is recovered (Figure \ref{management}). Thus when thresholds are in place, the harvesting rate no longer 
determines the critical rate of environmental shift $c^*$. We also examined the effect of marine protected 
areas (MPAs) on the population's persistence to see whether it might extend the range of harvesting and 
climate change parameters where the fish population could survive. With MPAs in place, the population had a 
slightly higher abundance along the edges of the patch where the population is limited by harvesting, which 
translated into a slightly increased critical harvest rate (Figure \ref{management}). Additionally MPAs increased 
overall catch at the highest harvest rates under which the population could survive (Figure \ref{management}).

@@

\end{flushleft}
\end{spacing}

>>>>

%\begin{spacing}{1.9}
%\begin{flushleft}

@@

We added harvesting pressure by harvesting a constant proportion of the population, in order to confirm our analytical results. We extended our work by evaluating the effect of a threshold harvest rule and marine protected 
areas (MPAs). With a threshold rule, we evaluated the population at each point in space to determine how 
much harvesting should occur. If the population abundance was below the designated threshold, no 
harvesting occurred. If the population exceeded the threshold, then a proportion of the `surplus' individuals 
were harvested

MPAs are a form of management designed to check the impact of fishing on targeted populations and are typically designed to meet either conservation of fishery management goals \citep{Agardy1994, HollandBrazee1996, Gainesetal2010a}. To implement an MPA management strategy in our model, we examine the effect of both of these commonly advocated approaches. While both conservation and fisheries oriented MPA schemes align in their goal of maintaining a sustainable fished population, they differ in desired level of adult spillover. Fisheries-oriented MPAs are often designed such that they maximize adult spillover into fishable areas by creating many small reserves closely spaced \citep{HastingsBotsford2003}. The converse of this is the goal of conservation-oriented MPAs which seek to reduce adult spillover by minizing the ratio between the reserve edge length relative to area protected \citep{Gainesetal2010a}.

Networks of MPAs were introduced into our simulations by designating segments of space in which harvesting was forbidden (i.e. harvesting rates were equal to $0$). Conservation-oriented MPAs, are frequently large and rarely part of a larger network of reserves \citep{HastingsBotsford2003}. For solitary reserves to be successful at protecting target species, they must encompass self-sustaining fish populations \citep{HastingsBotsford2006, Gainesetal2010a}. As such modeling studies estimate that isolated reserves must be at least as large as the average dispersal distance for the targeted fish species \citep{Lockwoodetal2002, HastingsBotsford2003, Botsfordetal2001, Gainesetal2010}. To implement conservation MPAs we created reserves with a length of 4 times the average dispersal distance and had a distance of 8 times the average dispersal distance between them to ensure that populations would be self sustiaining and not dependent on other dispersal for other reserves \citep{Lockwoodetal2002}.

Previous work has shown that if MPAs are to benefit fisheries, the reserves should be broken into a network, closely spaced to maximize adult spillover into fishable areas and export of larvae from reserve to reserve \citep{ HastingsBotsford2003, Gaylordetal2005, Gainesetal2010a}. To mimic this management scheme, MPAs had a length of $\tfrac{1}{3}$ of the average dispersal distance and had a distance of $\tfrac{2}{3}$ of the average dispersal distance between them.

@@

We found that when thresholds are in place, the harvesting rate no longer determines the critical rate of environmental shift $c^*$ (Figure \ref{management}). We also examined the effect of marine protected  areas (MPAs) on the population's persistence to see whether it might extend the range of harvesting and  climate change parameters where the fish population could survive. With MPAs in place, the population had a  slightly higher abundance along the edges of the patch where the population is limited by harvesting, which  translated into a slightly increased critical harvest rate (Figure \ref{management}). Additionally MPAs increased overall catch at the highest harvest rates under which the population could survive (Figure \ref{management}).

@@

%\end{flushleft}
%\end{spacing}
